### 2023-05-16 editorial-materials/EPB-2022-0116.R1_response_to_reviewer.Rmd

Barcelona_District <- merge(Barcelona_District,Data.bar,by="District")
q <- quantile(Barcelona_District$Por)
Barcelona_District$Quantile<- as.factor((Barcelona_District$Por > q[2]) + (Barcelona_District$Por > q[3]) +(Barcelona_District$Por >= q[4]) + 1)
levels(Barcelona_District$Quantile) <- c("(4.7%,5.7%]","(5.7,6.9]","(6.9,8.2]","(8.2,14.9]")
plot.d1 <- ggplot(data = Barcelona_District) +
  geom_sf(aes(fill = Quantile),size=.2) +
  theme_bw(base_size = 6) +
  scale_fill_discrete("") +
    scale_fill_manual(name = "",values=c("#D4E7F1","#6DAFD3","#2470B2","darkblue")) +
  theme_bw(base_size = 6) +
  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"),legend.position = "bottom",
        legend.key.size = unit(.2, 'cm'),text = element_text(size=4))

Madrid_District <- merge(Madrid_District,Data.mad,by="District")
q <- quantile(Madrid_District$Por)
Madrid_District$Quantile<- as.factor((Madrid_District$Por > q[2]) + (Madrid_District$Por > q[3]) +(Madrid_District$Por >= q[4]) + 1)
plot.d2 <- ggplot(data = Madrid_District) +
  geom_sf(aes(fill = Quantile),size=.2) +
  theme_bw(base_size = 6) +
  scale_fill_manual(name = "",values=c("#D4E7F1","#6DAFD3","#2470B2","darkblue")) +
  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"),legend.position = "bottom",
        legend.key.size = unit(.2, 'cm'),text = element_text(size=4))

Valencia_District <- merge(Valencia_District,Data.val,by="District")
q <- quantile(Valencia_District$Por)
#levels(B$Quartile) <- c("Q1: (1200,4050]","Q2: (4050,5450]","Q3: (5450,8290]","Q4: (8290,830000]")
Valencia_District$Quantile<- as.factor((Valencia_District$Por > q[2]) + (Valencia_District$Por > q[3]) +(Valencia_District$Por >= q[4]) + 1)
plot.d3 <- ggplot(data = Valencia_District) +
  geom_sf(aes(fill = Quantile),size=.2) +
  theme_bw(base_size = 6) +
  ylim(39.405,39.52) +
  scale_fill_manual(name = "",values=c("#D4E7F1","#6DAFD3","#2470B2","darkblue"))+
  theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"),legend.position = "bottom",
        legend.key.size = unit(.2, 'cm'),text = element_text(size=4))
grid.arrange(plot.d1, plot.d2, plot.d3, ncol = 3, nrow = 1)
```
